\documentclass{myres}

\begin{document}
{\LARGE \bf Jiangchuan He}
\myline

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% contact %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{CONTACT \\INFORMATION}
{
	\mycontact{382 Joe Mccarthy Dr}{{\sl Tel: }(716) 604-7268}
	\mycontact{Amherst, NY 14228}{{\sl Email: }\myemail{jiangchu@buffalo.edu}}

	\mycontact{}{{\sl Website: }\mywebsite{http://www.buffalo.edu/~jiangchu/}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{EDUCATION}
{\textbf{M.S., Computer Science, University at Buffalo \hfill Sep.2013-Dec.2014} 		
\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
	\item[]GPA:3.3/4.0
	\item[]Coursework: Algorithm Analysis and Design, Machine Learning, Pattern Recognition, Operating System, Distributed System,
		Fundamental of Programming Language
\end{itemize}
\par
\smallskip
\textbf{B.E., Software Engineering, Sichuan University \hfill Sep.2009-Jun.2013} 		
\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
	\item[]GPA:3.3/4.0
	\item[]Coursework: Discrete Mathematics, Data Structure, Database Systems, Computer Architecture, System Programming,
		Computer Network
\end{itemize}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% course projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{IMPRESSIVE \\ PROJECTS}
{
	\textbf{OS161 Kernel Implementation}
	\par
	\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
		\item Designed Synchronization Primitives, System Calls and Process Support, Virtual Memory
			which supports swapping.
		\item Used Git to manage source code and collaborate with parnter.
		\item Built everything from startup and completed all the test cases. 
	\end{itemize}
	\par
	\smallskip
	\textbf{Distributed Hash Table Implementation}
	\par
	\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
			\item Implemented a Dynamo-style distributed hash table using 5 android emulators.
			\item The program supports all Dynamo functions such as partition, replication and failure handling.
	\end{itemize}
	\par
	\smallskip
	\textbf{Gesture Recognition using Hidden Markov Model}
	\par
	\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
			\item Used Spatial Clustering to extract observation sequences.
			\item Implemented Hidden Markov Model and used it to give prediction with almost 90\% correct rate.
	\end{itemize}	
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% awards %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{HONORS AND\\ AWARDS}
{
	\textbf{Oracle ThinkQuest Competition(Global Top 10\%) \hfill  Jun.2012}
	\par
	We implemented a windows application which allows user to control multiple
	computers in a group using one mouse and keyboard device. The features
	include directly dragging files among screens and clipboard data sharing. I am the
	major designer responsible for implementing application structure as well as the
	features mentioned above.
	\par
	\smallskip
 	\textbf{Chinese Sciences Cup(National Top 13 teams) \hfill Sep.2011}
	\par
	We designed and implemented the early version of the multiple computers mouse
	and keyboard sharing application. I launched this project in windows
	MFC framework. I designed several key tricks such as using transparent window
	and global hook to capture interactive messages.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% working experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{WORKING \\ EXPERIENCE}
{
	\textbf{GSK CNC Equipment Co., Ltd.\hfill Jun.2010-Aug.2010}
	\par
	{\it Software Engineer Intern}
  \begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
			\item Learned to use ARM Cortex-M3 processor and STM32 development board
			\item Successfully porting x86 uC/OS kernel to ARM Platform
			\item Implemented a two-axis machine tool control program based on
				STM32F103 development board, which helped me gain the excellent award in my
				Undergraduate Final Project.
	\end{itemize}
	\par
	\smallskip
	\textbf{Sichuan Hwadee Information and Technology Co., Ltd. \hfill Jun.2012-Aug.2012}
	\par
	{\it Web Developer Intern}
  \begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
		\item Designed and Implemented a House-Selling Website.
		\item My task was to write and test front end.
	\end{itemize}
	\par
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% computer skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{COMPUTER \\ SKILLS}
{
	Language: x86 and Thumb Assembly, C/C++, Java, Shell Script, Python, Javascript, HTML, CSS
	\par
	Tools: Vim, Eclipse, Visual Studio, uVision, \LaTeX
	\par
	Operating System: Mac OS X, Linux, Windows, uC/OS
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% other experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\mysection{OTHER \\ EXPERIENCE}
%{
%
%}
\end{document}
