\documentclass{myres}

\begin{document}
{\LARGE \bf Jiangchuan He}
\myline

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% contact %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{CONTACT \\INFORMATION}
{
	\mycontact{08E Flickinger Ct}{{\sl Tel: }(716) 604-7268}
	\mycontact{Buffalo, NY 14228}{{\sl Email: }\myemail{jiangchu@buffalo.edu}}

%	\mycontact{}{{\sl Website: }\mywebsite{http://www.buffalo.edu/~jiangchu/}}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% objective %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{OBJECTIVE}
{
	To find a internship or full time software engineer job after Dec.2014 with preferred work locations in
	TX, CA, Fl or other locations required by company.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{EDUCATION}
{\textbf{M.S., Computer Science, University at Buffalo \hfill Sep.2013-Dec.2014(expected)} 		
\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
	\item[]GPA:3.29/4.0
	\item[]Coursework: Algorithm Analysis and Design, Machine Learning, Pattern Recognition, Operating System, Distributed System,
		Fundamental of Programming Language
\end{itemize}
\par
\smallskip
\textbf{B.E., Software Engineering, Sichuan University \hfill Sep.2009-Jun.2013} 		
\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
	\item[]GPA:3.3/4.0
	\item[]Coursework: Discrete Mathematics, Data Structure, Database Systems, Computer Architecture, System Programming,
		Computer Network
\end{itemize}

}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% awards %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{HONORS AND\\ AWARDS}
{
	\textbf{Oracle ThinkQuest Competition(Global Top 10\% teams) \hfill  Jun.2012}
	\par
 	\textbf{Chinese Sciences Cup(National Top 13 teams) \hfill Sep.2011}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% working experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{WORKING \\ EXPERIENCE}
{
	\textbf{GSK CNC Equipment Co., Ltd.\hfill Jun.2010-Aug.2010}
	\par
	{\it Software Engineer Intern}
  \begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
			\item Learned to use ARM Cortex-M3 processor and STM32 development board.
			\item \textbf{Successfully porting} x86 $\mu$C/OS kernel to ARM Platform.
			\item Developed a two-axis machine tool \textbf{control software} based on
				STM32F103 development board, which was awarded in
				Undergraduate Final Project.
	\end{itemize}
	\par
	\smallskip
	\textbf{Sichuan Hwadee Information and Technology Co., Ltd. \hfill Jun.2012-Aug.2012}
	\par
	{\it Web Developer Intern}
  \begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
		\item Designed and built a House-Selling Website.
		\item Wrote and maintained project documents.
	  \item Implemented and tested front end code.
	\end{itemize}
	\par
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% course projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{PROJECTS}
{
	\par
	\textbf{Mouse and Keyboard Sharing Application\hfill Feb.2011}
	\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
		\item Designed a Windows MFC Application which allows user to control multiple computers in a group using one mouse and keyboard device. 
		\item The features included directly \textbf{dragging files among screens} and clipboard data sharing. 
		\item I was the major designer responsible for implementing \textbf{application structure} as well as the
					features mentioned above.
	\end{itemize}

	\par
	\smallskip

%	\textbf{Concurrent Programming in Java and SML\hfill Sep.2013}
%	\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
%		\item Implemented Coarse-grained and Fine-grained locking and improved their performance.
%		\item Given test on Doubly linked list with intensively frequent insert and delete operations.
%		\item Implemented message passing using Standard ML(SML/CML) language.	
%	\end{itemize}

%	\par
%	\smallskip

	\textbf{Harvard OS/161 Kernel Implementation \hfill Feb.2014}
	\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
			\item Developed a \textbf{multicore} operating system kernel which runs on MIPS r2000 simulator.
		\item The work included implementing Synchronization Primitives, System Calls and Process Support, Virtual Memory
			which \textbf{supports swapping}.
		\item Used Git to manage source code and shell scripts to improve efficiency.
		\item Built everything from the beginning and completed all the test cases. 
	\end{itemize}

	\par
	\smallskip

	\textbf{Pen-gesture Recognition with Hidden Markov Models \hfill Apr.2014}
	\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
			\item Designed spatial clustering algorithm to extract observation sequences.
			\item Implemented Hidden Markov Model and used it to give prediction with almost 90\% correct rate.
			\item Designed and implemented prediction algorithm also using Dynamic Time Warping and Viterbi decoding. 
	\end{itemize}	

	\par
	\smallskip

	\textbf{Amazon Dynamo(Distributed Key-Value Storage) \hfill May.2014}
	\begin{itemize}[topsep=0pt, leftmargin=0.2in] \itemsep -5pt
			\item Created a Dynamo-style key-value storage using five Android Emulators.
			\item Implemented the functionality of partition, replication and \textbf{failure handling}.
			\item Provided both availability and linearizability at the same time using Quorum replication. 
	\end{itemize}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% computer skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\mysection{COMPUTER \\ SKILLS}
{
	Language: x86 and Thumb Assembly, C/C++, Java, Shell Script, Python, Javascript, HTML, CSS
	\par
	Tools: Vim, Eclipse, Visual Studio, $\mu$Vision, \LaTeX
	\par
	Operating System: Mac OS X, Linux, Windows, $\mu$C/OS
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% other experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\mysection{OTHER \\ EXPERIENCE}
%{
%
%}
\end{document}
